% !TEX root = ba_doc.tex
\begin{abstract}
\begin{markdown}

\noindent With ZHAWo we want to provide students of the Zurich University of Applied Sciences (ZHAW) with a single application for their daily study tasks. Students need to be able to quickly look up their timetable and what lunch menus are available at their campus mensa. While these functions are provided by the university's official app, we want to provide a consistent user experience among different platforms using Progressive Web App technologies. Additionally, ZHAWo offers an interface to search for free rooms. This function was previously provided by an app that is no longer available and was extensively used to find rooms for projects or study groups to work in environment less busy than the usually crowded official work spaces. We also integrated news and events from the Verein Studierende ZHAW (vszhaw) into ZHAWo to provide students with easier access to information about events and services. 
A student survey confirmed the high demand for the room search feature. Our application received good ratings for usability, performance and design.

\noindent As a secondary objective, we evaluated the practicability of using cross platform web technologies to build a Progressive Web App. It enabled us to apply an agile development approach with fast prototyping of new features while still providing an application with the functionalities and feel that users expect from a native app. With this approach, we also avoided having to maintain multiple code bases for different platforms and mixing different technologies for frontend and backend.
Progressive Web App technology is still very new. There are notable differences in support and implementation. As the the technology matures, we expect it to be a viable alternative to building native applications.

\end{markdown}
\end{abstract}
