% !TEX root = pa_doc.tex
\begin{abstract}
\begin{markdown}

\noindent With ZHAWo we want to provide students of the Zurich University of Applied Sciences (ZHAW) with a single application where they can complete the most important tasks in their daily studies. Students need to be able to quickly look up their timetable, what lunch menus are available at their campus mensa and where a certain building or room can be found. While these functions are provided by the university's official app, we provide a consistent user experience among different platforms using Progressive Web App technologies. Additionally, with ZHAWo we provide students with an interface to search for free rooms. This function was previously provided by an app that is no longer available and was extensively used to find rooms for projects or study groups to work in environment less busy than the usually crowded official work spaces.

\noindent We also integrated news and events from the Verein Studierende ZHAW (vszhaw) into ZHAWo to provide students with easier access to information about events and services.

\noindent Using the JavaScript frameworks React for the frontend and Express for the backend in combination with Progressive Web App enables us to apply an agile development approach with fast prototyping of new features while still providing an application with the functionalities and feel that users expect from a native app. With this approach, we also avoid having to maintain multiple code bases for different platforms and mixing different technologies for frontend and backend. As a consequence, extending and improving the application's functionality can be done at a high velocity.

\end{markdown}
\end{abstract}
